Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-13 RR_manuscript/Draft_RR.Rmd
add info on divergent transitions in RR #288

Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, might have been inappropriate.
Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs. milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
Model refitting also constituted a way of validating the reported analyses, a step recommended by @aczel2021.
Details about the refitting procedure can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow>.
Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file  and variable naming conventions and the use of treatment contrasts instead of sum coding.
All models converged ($\hat{R}$ was approximately 1) and only some had a small number of divergent transitions which were not deemed problematic (range XXX).

>>>>

Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, might have been inappropriate.
Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs. milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
Model refitting also constituted a way of validating the reported analyses, a step recommended by @aczel2021.
Details about the refitting procedure can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow>.
Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file  and variable naming conventions and the use of treatment contrasts instead of sum coding.
All models converged ($\hat{R}$ was approximately 1).
Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 143 (143 represents 3.58% of total number of samples), which the authors deemed not to be problematic.
